Plots for Latent Hawkes Paper

### 2020-12-01 output_scripts/Paper_Plots.Rmd
update plots

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=4,fig.width=8}
sim_data_path <- "../output/sims/sims_m3_dc/"

@@

```{r fig4b-recover-latent-states,fig.width=8,fig.height=4}
y.ub <- c(15,15,15)#c(130,72,31)
x_events <- 135#150
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 140#160#200#130
my.long.x <- 140#205#134.5
legend.x <- c(40,40,40)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(10,10,10)#c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

@@

legend(legend.x[2]-35,
       legend.y[2]+2,c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(8,legend.y[2] - 2, pch = 1, cex = 2, col = "blue")
points(10,legend.y[2] - 2, pch = 16, cex = 2, col = "blue")

@@

# model3
########
par(mar = c(0,0.3,1,0.1))
drawUniMMHPIntensityPaper(true.object,
                          simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[3],
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawUniMMHPIntensityPaper(object_hat,
                          simulation = list(
  x=state.est.latent.mmhp.new$x.hat,                                          
  z=state.est.latent.mmhp.new$z.hat,
  tau=test.mmhp$tau,zt=test.mmhp$zt,
  lambda.max=test.mmhp$lambda.max),
                          yupper=y.ub,add=TRUE,
                          color=add.alpha(model_colors[3],
                                      alpha=line.alpha[2]),
  line.width=line.wdth[2])
legend(legend.x[3],legend.y[3],"C-MMHP",
       col = model_colors[3],
       y.intersp=0.88,x.intersp=0.1,bty = "n",
       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)

legend(legend.x[3]-30,legend.y[3]+2, c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.88,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

## top
mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)
```

@@

```{r fig-7-prMatrix-Cohort5, fig.height=7}
# current_cohort <- 5

@@

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )

@@

```{r fig-matrix-structure-score}
library(NMF)
source(here("lib","residualStructureScore.R"))

@@

struct_plot %>% 
  ggplot(aes(Method,Score)) + geom_boxplot() +
  facet_wrap(~Pos_Neg, scales = "free") + theme_minimal()

>>>>

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=6,fig.width=8}
sim_data_path <- "../output/sims/sims_m3_dc/"

@@

```{r fig4b-recover-latent-states,fig.width=8,fig.height=5}
y.ub <- c(15,15,15)#c(130,72,31)
x_events <- 190#135#150
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#160#200#130
my.long.x <- 205#205#134.5
legend.x <- c(150,150,150)#c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(12,12,12)#c(15,12,15)#c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m1$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now ###
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events),#200
        c(0,delta.positive,0),col=positive.col,border=NA)

@@

legend(legend.x[2]-45,
       legend.y[2]+2,c("State 0/1 events","State change point"),
       col = c(NA,"red"),
       y.intersp=0.85,x.intersp=-0.1, bty = "n",
       pch = c(NA,4), pt.cex = c(NA,2), cex=legend.cex,
       lty = c(NA,NA), lwd=c(NA,4))
points(110,legend.y[2] - 3, pch = 1, cex = 2, col = "blue")
points(113,legend.y[2] - 3, pch = 16, cex = 2, col = "blue")

@@

plot(lambda.true$time.vec,delta.lambda,xlim=c(0,my.xlim), 
     ylim=c(-2,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m2$lambda.t-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), #200
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

# model3
########
par(mar = c(0,0.3,1,0.1))
drawUniMMHPIntensityPaper(true.object,
                          simulation=fixStateTransition(test.mmhp),
                          yupper=y.ub[3],
                          color=add.alpha("black", alpha=line.alpha[1]),
                          line.width=line.wdth[1],
                          y.ratio=-0.05, min.y=-2, min.x=0, max.x=my.xlim, 
                          box.type="n")
drawUniMMHPIntensityPaper(object_hat,
                          simulation = list(
                            x=state.est.latent.mmhp.new$x.hat,                                          
                            z=state.est.latent.mmhp.new$z.hat,
                            tau=test.mmhp$tau,zt=test.mmhp$zt,
                            lambda.max=test.mmhp$lambda.max),
                          yupper=y.ub,add=TRUE,
                          color=add.alpha(model_colors[3],
                                          alpha=line.alpha[2]),
                          line.width=line.wdth[2])
legend(legend.x[3],legend.y[3],"C-MMHP",
       col = model_colors[3],
       y.intersp=0.6,x.intersp=0.1,bty = "n",
       lty =1, lwd = 5,cex=legend.cex,seg.len=1)
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0.5,tick=T,labels=rep("",2),lwd=0.5,lwd.ticks=0,lty=3)

legend(legend.x[3]-45,legend.y[3]+2, c("Overestimation","Underestimation"),
       col = c(positive.col,negative.col),
       y.intersp=0.6,x.intersp=0.5,bty = "n",
       lty = c(1,1), lwd = c(10,10), cex=legend.cex,seg.len=0.8)

## delta lambda
par(mar = c(0,0.3,0,0.1))
plot(0,0,xlim=c(0,my.xlim), ylim=c(-2,4), type="n",
     bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
delta.lambda <- lambda.m3-lambda.true$lambda.t
delta.positive <- delta.lambda
delta.positive[delta.positive<0] <- 0
delta.negative <- delta.lambda
delta.negative[delta.negative>0] <- 0
### hiding these for now
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.negative,0),col=negative.col,border=NA)
polygon(c(0,lambda.true$time.vec,x_events), # 200 
        c(0,delta.positive,0),col=positive.col,border=NA)
# segments(0,0,my.xlim,0,col="gray45")
## draw box
axis(1,at=c(-2,my.long.x),col="gray35",
     line=0,tick=T,labels=rep("",2),lwd=0.7,lwd.ticks=0)

## top
mtext(text="(b)",side=3,line=0.8,outer=TRUE,cex=2.5,font=2)
## bottom
mtext(text="Time",side=1,line=2,outer=TRUE,cex=2.25)
## left
mtext(text="Intensity",side=2,line=0.6,outer=TRUE,cex=2.25)

@@

```{r fig-7-prMatrix-Cohort5, fig.width=7, fig.height=7}
current_cohort <- 5

@@

matrix_lst_plot <- list(
                        indep_pr[rev(expert_rank_10[[current_cohort]]),
                                                                   expert_rank_10[[current_cohort]]],
                        m1_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m2_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]],
                        m3_pr[rev(expert_rank_10[[current_cohort]]),
                                                                 expert_rank_10[[current_cohort]]]) 
#cat("Cohort ",current_cohort,"\n",sep="")
myMultiMatrixPlot(X=matrix_lst_plot,no_matrix=4,n_row=2,
                  xLabels=expert_rank_10[[current_cohort]],
                  yLabels=rev(expert_rank_10[[current_cohort]]),
                  min=-80,max=80,axis_cex=2,title_cex = 1.8,
                  colorPalette="RdBu",if.emp=FALSE,
                  #legend.mar=c(0.5,.5,0.5,0.5),
                  title_lst=list("I-MMHP","C-HP","C-DCHP","C-MMHP"), 
                  #title_lst = list("I-MMHP"),
                  col_axis=c(-80,-40,0,40,80), fake_matrix=FALSE,
                  matrix.mar=c(2.5,2.5,2.5,1)
                  )
mtext(text="(a)",side=3,line=0.5,outer=TRUE,cex=2.5,font=2)

@@

```{r fig-7b-matrix-structure-score, fig.width=7, fig.height=7}
library(NMF)
source(here("lib","residualStructureScore.R"))

@@

box_cols <- col_df %>% 
  filter(method %in% c("I-MMHP","C-HP","C-DCHP","C-MMHP")) %>%
  pull(cols)

struct_plot %>% 
  ggplot(aes(Method,Score, fill = Method)) + geom_boxplot() + 
  scale_fill_manual(values = box_cols) +
  ggtitle("(b)") +
  facet_wrap(~Pos_Neg) + theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
              text = element_text(size = 20),
              axis.text.y =element_text(size = 11),
              axis.text.x = element_blank(),
              axis.title.x=element_blank() )
